Natural selection in contemporary humans is linked to income and substitution effects

### 2020-12-22 why-natural-selection.Rmd
Fix reverse-coded rgs
Tweaks

```{r plot-n-partners, fig.cap = "Selection effects by number of sexual partners, household type, and age at first live birth.", fig.subcap = c("Lifetime number of sexual partners", "Household type", "Age at first live birth, females"), fig.ncol = 1, fig.align = "center"}

@@

```{r plot-age-flb, fig.cap = "Selection effects by age at first live birth, and controlling for age at first live birth (women only).", fig.ncol = 1,  fig.subcap = c("Effect sizes by age at first live birth terciles", "Effect sizes controlling for age at first live birth. Effect sizes without controls (for women only) shown for comparison."), fig.align = "center"}

@@

Another way to examine the "earnings" theory of natural selection is to compare
selection effects of polygenic scores with their genetic correlation with educational
attainment (EA3). Since EA3 strongly predicts earnings, if earnings drives
differences in fertility, we'd expect a correlation between the two sets of
results. Figure \@ref(fig:plot-rgs-by-effect-size) shows this is so: the 
correlation is `r rgs_cor$estimate`. Genetic
correlations were calculated using LD score regression from GWAS summary
statistics.

>>>>

```{r plot-n-partners, fig.cap = "Selection effects by number of sexual partners and household type.", fig.subcap = c("Lifetime number of sexual partners", "Household type"), fig.ncol = 1, fig.align = "center"}

@@

```{r plot-age-flb, fig.cap = "Selection effects by age at first live birth, and controlling for age at first live birth (women only).", fig.ncol = 1,  fig.subcap = c("Effect sizes by age at first live birth terciles (women only)", "Effect sizes controlling for age at first live birth. Effect sizes without controls (for women only) shown for comparison."), fig.align = "center"}

@@

Another way to examine the "earnings" theory of natural selection is to compare
selection effects of polygenic scores with their genetic correlation with educational
attainment (EA3). Since EA3 strongly predicts earnings, if earnings drives
differences in fertility, we'd expect a correlation between the two sets of
results. Figure \@ref(fig:plot-rgs-by-effect-size) shows this is so: the 
correlation, after excluding EA2, is `r rgs_cor$estimate`. Genetic
correlations were calculated using LD score regression from GWAS summary
statistics.
